%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
\cventry
{DevOps Tech Lead} % Job title
{Getninjas} % Organization
{São Paulo, SP} % Location
{September 2022 - Present} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
   \item {Responsible for organizing Jira and team tasks}
   \item {Mentoring and leading the platform team}
   \item {1-1 feedback sessions}
   \item {Mentoring in technical and architectural decisions}
   \item {Cloud management (AWS and GCP)}
   \item {Management and deployment of Kubernetes}
   \item {Automated processes, leadership, and more than 8 other competencies}
  \end{cvitems}
}

\cventry
{Senior DevOps Engineer} % Job title
{Getninjas} % Organization
{São Paulo, SP} % Location
{February 2020 - September 2022} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
   \item {Worked on creating, maintaining, and troubleshooting all aspects of the company's infrastructure, creating environments in IaC and ensuring their maintainability, speed, and optimized resource usage}
   \item {Development in Python, Groovy, Golang, and Shell script (with occasional Ruby)}
   \item {Development and use of CI/CD pipelines using Jenkins and Drone}
   \item {Creation of cloud resources using IaC (Terraform)}
   \item {Creation and maintenance of Kubernetes resources (Helm, Istio, etc.)}
   \item {Advanced use of CDN to speed up applications and save on infrastructure costs}
   \item {FinOps - Advanced monitoring of cloud resource usage}
   \item {ChatOps - Using Slack as the central management tool for infrastructure resources}
   \item {Troubleshooting web applications}
   \item {Cloud environments (AWS and GCP)}
   \item {Migration of services to the cloud and Kubernetes}
   \item {Observability with Prometheus, Thanos, Grafana, Kibana (Elastic)}
   \item {APM using New Relic}
   \item {Log management using the Elastic Stack (and syslog-ng)}
  \end{cvitems}
}


\cventry
    {System Architecture Specialist} % Job title
    {Locaweb} % Organization
    {São Paulo, SP} % Location
    {January 2019 - February 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
       \item {I work on designing, creating, and applying best practices in the creation of architectures within AWS, including automation, infrastructure as code, migration from on-premises to cloud, troubleshooting, fine-tuning, and documentation, always aiming to maintain applications in the best possible architecture, considering performance and final cost for the customer:}
       \item {Design and implementation of AWS architectures.}
       \item {Migration and architecture of services in AWS:}
       \item \quad {Beanstalk}
       \item \quad {ECS}
       \item \quad {EC2}
       \item \quad {S3}
       \item \quad {RDS}
       \item \quad {Among others...}
       \item {Administration of batch mesh migration with Control-M.}
       \item {Infrastructure as code using Terraform.}
       \item {Automation with Ansible and Python.}
       \item {Development of scripts in Python (boto3, Lambda).}
       \item {Automation of build pipelines (CI and CD) with Jenkins and AWS CodeBuild.}
       \item {Development of plugins for Jenkins.}
       \item \quad {Deployment authorization (Python).}
       \item \quad {Error and log notification (Java).}
       \item {Web application architecture (WAF, CDN).}
       \item {Development of Shell Script scripts.}
      \end{cvitems}
    }


  \cventry
    {Software Engineer} % Job title
    {GoCache CDN} % Organization
    {São Paulo, SP} % Location
    {January. 2018 - January 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
       \item {Api development with python and lua ( Openresty )}
       \item {Openresty deployment, maintenance and plugin development}
       \item {Api and tools development with Golang}
       \item {Server automation with Salt}
       \item {First CI and CD pipelines for all the apps }
       \item {Build automation with Jenkins}
       \item {Web application troubleshooting ( mostly php, but a lot others )}
       \item {Linux kernel troubleshooting}
       \item {Web application performance tunning using CDN's and other observability methods}
      \end{cvitems}
    }

  \cventry
    {DevOps Engineer} % Job title
    {Bankfacil/Creditas} % Organization
    {São Paulo, SP} % Location
    {June. 2016 - July. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Support and enhance our web architecture with new technologies and tools}
      \item {Server automation with puppet and ansible}
      \item {Developer tooling sollutions with python, docker and ECS}
      \item {Web and tool development with Python, Ruby and shell script}
      \item {Ruby on rails development and troubleshooting}
      \item {Development and data modelling with Snowplow}
      \item {Snowplow pipepiline development}
      \item {Database administration: PostgreSQL, MySQL e Redshift}
      \item {Web application performance tunning using CDN's and other observability methods}
\end{cvitems}
    }

%---------------------------------------------------------
\cventry
{DevOps Engineer} % Job title
{Bankfacil/Creditas} % Organization
{São Paulo, SP} % Location
{June 2016 - July 2017} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Support and improve the AWS/DigitalOcean cloud environment}
    \item {Server automation with Ansible and Puppet}
    \item {Development of solutions using Docker and ECS}
    \item {Development in Ruby, Python, and Shell script}
    \item {Development and bug fixing of Ruby on Rails applications}
    \item {Development and data modeling in SnowPlow}
    \item {Development of auxiliary tools for SnowPlow}
    \item {Database administration: PostgreSQL, MySQL, and Redshift}
    \item {Web application analysis and troubleshooting}
  \end{cvitems}
}

  %---------------------------------------------------------
  \cventry
  {Senior Development/Infrastructure Analyst} % Job title
  {Light Cloud Internet Services \(Midgar\)} % Organization
  {São Paulo, SP} % Location
  {September. 2015 - April. 2016} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Development and deployment of Linux architectures.}
      \item {Development of a dynamic platform with Docker.}
      \item {Development of admin tools in Python.}
      \item {Development of an email platform with open source technologies.}
      \item {Implementation of NFS clusters with Pacemaker and Drbd.}
      \item {Administration of MySQL/MariaDB servers and clusters.}
      \item {Performance tuning for php, rails, and nodejs apps.}
      \item {Development of web services in Python.}
      \item {Administration of BIND servers and DNS splits with Active Directory.}
      \item {Caching of applications with Nginx, Varnish, and memcached.}
      \item {Caching and KV store with Redis.}
      \item {Administration of VMware hosts via Vcenter.}
      \item {Development of load testing tools in Python.}
      \item {WAN and LAN network administration.}
      \item {Development of shared and isolated SSH structure.}
      \item {Development of an administration panel.}
      \item {RabbitMQ and RQ message queues.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Infrastructure Analyst / DevOps} % Job title
  {Fundação Casper Libero (TVGazeta)} % Organization
  {São Paulo, SP} % Location
  {February. 2015 - September. 2015} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Development and deployment of Linux architectures.}
      \item {Implementation of NFS clusters with Pacemaker and Drbd.}
      \item {Administration of MySQL/MariaDB servers and clusters.}
      \item {Performance tuning for php, rails, and nodejs apps.}
      \item {Development of web services in Python.}
      \item {Administration of BIND servers and DNS splits with Active Directory.}
      \item {Monitoring with Icinga and New Relic.}
      \item {Caching of applications with Nginx, Varnish, and memcached.}
      \item {Caching and KV store with Redis.}
      \item {Administration of VMware hosts via Vcenter.}
      \item {Development of load testing tools in Python.}
      \item {WAN and LAN network administration.}
      \item {Server automation with Puppet.}
      \item {Continuous Integration (CI) of apps with Jenkins.}
      \item {Development of PHP/Python/Shell scripts.}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
{System Analyst / DevOps} % Job title
{Credibilit Tecnologia} % Organization
{São Paulo, SP} % Location
{July 2014 - January 2015} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Development and deployment of AWS architectures.}
    \item {Planning and migration of infrastructures to AWS.}
    \item {Linux server administration (Apache, Nginx, Varnish).}
    \item {Development of web services in Python.}
    \item {Development of tools for operation and code deployment.}
    \item {Environment monitoring and service integration with NewRelic (APM, Insights, Browser, Servers).}
    \item {Log management and sending to Loggly.}
    \item {Creation and administration of MongoDB clusters.}
    \item {Creation and administration of Docker applications.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{System Analyst / Developer} % Job title
{Polimetri Industria Metalurgica} % Organization
{Mauá, SP} % Location
{February 2014 - July 2014} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Development and maintenance of Delphi applications (Legacy systems).}
      \item {Rewrite of ERP tool from Delphi to Python.}
      \item {Development in Python with Flask and pywin32.}
      \item {Service integration with Active Directory.}
      \item {Migration of Windows servers to Linux.}
      \item {Database administration (Informix, PostgreSQL, MySQL, and SQL Server).}
      \item {Introduction of caching in legacy applications (Redis and Memcached).}
      \item {Development for Windows CE (Delphi XE6). Creation of VPN infrastructure.}
      \item {Migration and installation of email servers.}
      \item {Infrastructure virtualization with VMware and VirtualBox.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{System Administrator \& DevOps} % Job title
{UolHost} % Organization
{São Paulo, SP} % Location
{August 2012 - February 2014} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Development of the new UOLHOST hosting platform.}
      \item {Automation with Puppet and CFEngine.}
      \item {Agile development with SCRUM.}
      \item {Maintenance and development for legacy platforms.}
      \item {Migration of legacy platforms.}
      \item {Development in Perl, Python, C, Lua, Shell script, and GO.}
      \item {Development of APIs/Webservices in Python and GO.}
      \item {Administration of NoSQL databases and web services like Redis and Memcache.}
      \item {Creation of automation services for Linux containers with LXC.}
      \item {Resource isolation by application and users (cgroups).}
      \item {Handling and generating statistics from large data sets.}
      \item {File Server on Solaris with NFS, ZFS, and Samba.}
      \item {Service integration with Active Directory.}
      \item {Administration of shared CPanel environment.}
      \item {Caching with Nginx and Memcached.}
      \item {Advanced Nginx administration with Lua, module creation (C).}
      \item {Advanced Apache administration and module creation (C).}
      \item {Kernel and driver level debugging.}
      \item {Collaboration with open source communities.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{System Analyst \& Developer} % Job title
{IMP TeleInformatica} % Organization
{São Caetano, SP} % Location
{September 2011 - May 2012} % Date(s)
{
\begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Implementation, configuration, and parameterization of Totvs Protheus.}
    \item {Development of tools in corporate environment using C\# and Python.}
    \item {User support for the Totvs Protheus system.}
    \item {Installation and maintenance of Linux servers.}
\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Infrastructure Technician} % Job title
{Totvs SA} % Organization
{São Paulo, SP} % Location
{August 2010 - August 2011} % Date(s)
{
\begin{cvitems} % Description(s) of tasks/responsibilities
  \item {Support to clients using their ERP in the data center.}
  \item {Implementation and configuration of applications, Microsiga Protheus, Logix, Serie 1 First.}
  \item {Maintenance of data center servers, cabling, networks, and activity monitoring.}
  \item {Development of service monitoring tools.}
  \item {Maintenance and implementation of database services (MSSQL and DB2).}
  \item {Development of automated system configuration tools.}
  \item {Maintenance of Linux servers.}
  \item {Implementation, maintenance, and monitoring of electronic invoice transmission service, TSS.}
  \item {Database migration.}
  \item {Testing and error identification.}
\end{cvitems}
}




%---------------------------------------------------------
\end{cventries}
